---
title: ""
output:
  html_document:
    theme: flatly
    highlight: tango
    toc: yes
    toc_float: yes
    collapsed: no
    number_sections: no
    toc_depth: 1
  pdf_document:
    toc: yes
    toc_depth: '1'
---



```{r load_packages, message=FALSE, warning=FALSE, include=FALSE} 
library(fontawesome)
```     



<!--\1   
```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE, warning=FALSE, cache=TRUE)
```
font-weight:bold; \1-->
 
```{css bullet-margin, echo = FALSE}
li {
    content:attr(aria-label);
    font-size:100%;
    margin-right:-10px;
}
``` 


# Personal Information 

Address        : Bergamo-Lombardia-Italy\
Email & Skype  : seymakalay@hotmail.com\
Driving Licence : B 

<!--\1Date of Birth   : 16.05.1987\
Mobile         : +39 338 9628589\
Marital Status : Single,\ \1-->


<!--\1 Place of Birth : Turkey-Istanbul\ \1-->

<!--\1
# Objectives
To work for the organization to the best of my knowledge and ability from where the organization could benefit from my programming, app building and machine learning skills. 
FOR ICON ION!!!
https://github.com/ionic-team/ionicons
Astronomy and Space Science
\1-->




# Education 
     
**Joint PhD in Applied Economics and Management (AEM)**\
University of Bergamo & Pavia (Italy), Sept 2017 - Feb 2022

**Master in Finance**\
University of Siena (Italy),  Nov 2013 - June 2016

<!--\1
**Certificate in Masters of Business Administration Program**\
University of Auburn (USA), Spring 2011 - Fall 2012\
\1-->

**Bachelor Degree in Physics**\
University of Istanbul (Turkey), Fall 2006 - Spring 2010                                                                             

# Experiences

**Associate Advanced Analytics Analyst** - Power BI Developer,\
<u>Mozarc Medical, Milan (Italy), Sep 2023 - Current.</u>\
<!--\1
Mozarc Medical, Milan (Italy), Sep 2023 - Current.\
- Data Analysis and Visualization: Assist in collecting, cleaning, and analyzing large datasets to identify trends, patterns, and insights. Develop visually appealing dashboards and reports using Power BI to effectively communicate findings to stakeholders.
\1-->
<body>
 <!--\1 <h3>Today's shopping list:</h3>\1-->
    <ul>
      <li>Assist in collecting, cleaning, and analyzing large datasets to identify trends, patterns, and insights.</li>
      <li>Develop visually appealing dashboards and reports using Power BI, Power Pivot, and DAX.</li>
      <li>Work closely with cross-functional teams to understand their analytical needs and provide insights.</li>
      <li>Develop data-driven strategies and recommendations to support business growth and efficiency.</li>
      <li>Ensure data quality and integrity by conducting data validation and cleansing.</li>
      <li>Help maintain data repositories.</li>
      <li>Implement data governance practices to ensure accuracy, consistency, and security.</li>
      <li>Collaborate effectively with team members across various departments.</li>
      <li>Communicate analytical findings, methodologies, and recommendations to stakeholders.</li>
    </ul>
</body>



**Assistant** - Market Research,\
<u>MPS - Evolving Marketing Research, Bergamo (Italy), April 2023- July 2023.</u>\
<!--\1  - Analyzing market research outcomes by creating databases and descriptive statistics.\1--> 
<body>
    <ul>
      <li>Prepare market research survey.</li>
      <li>Analyze and report market research outcomes, using Quantum Software.</li>
    </ul>
</body>




**Researcher** - Statistics,\
<u>University of Bergamo & Pavia (Italy), Sept 2017- Feb 2022.</u>\
<!--\1 - Implementing data manipulations, applying machine learning algorithms, and creating
interactive user faces^[Please see at: <a href="https://github.com/seymakalay" target="_blank">https://github.com/seymakalay</a> ].   \1-->
 <!--\1 application^[Please see at: https://github.com/seymakalay].\      
 to find out the probability of credit default\1-->
<body>
    <ul>
      <li>Manipulate and analyze large datasets to identify trends, patterns, and insights.</li>
      <li>Develop and implement machine learning models and algorithms, using R and Python.</li>
      <li>Adopt new tools, technologies, and methodologies to enhance the model outcomes.</li>
      <li>Create interactive user faces (such as R Shiny, HTML) to report the findings.</li>
    </ul>
</body>

 
**Intern** - Portfolio,\
<u>Ziraat Portfolio (Turkey), Jan 2016 - Sept 2016.</u>\
<!--\1  - Observed equity and bond market, familiar with the behavioral finance, created a statistical model to maximize the portfolio’s return and proved the model efficiency by tracing the data.\ \1--> 
<body>
    <ul>
      <li>Observe equity.</li> 
      <li>Be familiar with behavioral finance.</li>
      <li>Create a statistical model to maximize the portfolio‘s return, using VBA.</li>
      <li>Prove the model efficiency by tracking the data.</li>
    </ul>
</body>


**Intern** - Portfolio,\
<u>Invest-AZ (Turkey), Nov 2015 - Dec 2015.</u>\
<!--\1  - To analyze the companies by looking at their income statements 
and balance sheets to make sure it is beneficial to invest in those companies. \1--> 
<body>
    <ul>
      <li>Analyze listed companies by looking at their financial statements.</li>
      <li>Create reports to drive data-driven decision making for investors.</li>
    </ul>
</body>


**Intern** - Accounted,\
<u>Varkan Group (Turkey), Sept 2012 - Dec 2012.</u>\
<!--\1  - Have been effectively responsible of recording accounting cycle 
and kept tracking consistence balances on both suppliers and purchasers on the company’s system. \1--> 
<body>
    <ul>
      <li>Record accounting cycle.</li>
      <li>Keep tracking consistent balances on both suppliers and purchasers on the company‘s system.</li>
      <li>Track balances on both suppliers and purchasers on the company‘s system.</li>
    </ul>
</body>


<!--\1 
**Part time** - Real Estate\
Emlak Ada (Turkey), Jun 2007 - Jan 2010.\
- Was actively involved in the marketing and communications of the firm. Drafted contracts, scheduled meetings, handled negotiations, updated company website, collaborated with other real estate agencies, generated new solutions
and conducted research on customer needs and preferences.
\1-->

# Skills and Competencies 
<!--\1  **Languages:** Native in Turkish, advance in English, intermediate in Italian, beginner in Spanish.\     \1-->
<ul class="list-inline">
   <li> <u>**Languages:**</u>  </li>
   <li>&bull; Native in Turkish </li>
   <li>&bull; Fluent in English</li>
   <li>&bull; Advance in Italian</li>
   <li>&bull; Beginner in Spanish</li>
</ul>
<ul class="list-inline">
   <li> <u>**Computer Skills:** </u>  </li>
    <li> <u>*Advance:*</u>  </li>
    <li>&bull; DAX </li>
    <li>&bull; Power BI/ Query/Pivot </li>
    <li>&bull; R </li>
    <li>&bull; R Shiny Applications </li>
    <li>&bull;  LaTeX </li>
    <li>&bull; Microsoft Office </li>
   <li> <u>*Intermediate*</u>  </li>
    <li>&bull; HTML </li>
    <li>&bull; Python </li>
    <li>&bull; SQL </li>
    <li>&bull; Tableau </li>
   <li> <u>*Beginner:*</u>  </li>
   <li>&bull; Azure </li>
   <li>&bull; VBA </li>
   <li>&bull; Java </li>
   <li>&bull; Json </li>
   <li>&bull; Snowflake</li>
</ul>
<!--\1 Latex, Microsoft Office, R, Shiny Application. \1-->
<!--\1   <u>*New in:* </u> Html, Python, SQL, Java.\1-->
<ul class="list-inline">
<li> <u> **Soft Skills:** </u>  </li>
   <li>&bull; Time Management </li>
   <li>&bull; Problem Solving </li>
   <li>&bull; Reporting Skills </li>
   <li>&bull; Multitasking </li>
</ul>

<!--\1 
Creative, analytic thinker, problem solver, good at teamwork, interpersonal skills, determined, disciplined, accountable, highly motivated, responsible, strong work ethics, positive mindset, adaptable, rapid learning capability.
\1-->




# Projects

<u>**Interactive User Interfaces**</u>
<li><u><a href="https://seymakalay87.shinyapps.io/MapApp/" target="_blank">**MapApp:**</a></u> 
Conducting  an empirical study  <!--\1 based on anti money laundering, \1-->
using both supervised and unsupervised machine learning algorithms.</li>

<li><u><a href="https://seymakalay87.shinyapps.io/biblio/" target="_blank"> **Biblio:** </a></u> 
Reproducible bibliometric literature review.</li>

<li><u><a href="https://github.com/seymakalay/tp3" target="_blank"> 
**Tp3:**</a></u>
Conducting unsupervised machine learning algorithms (Tp3: runs from console). </li>

<u>**Viz**</u>
<li><u><a href="https://public.tableau.com/app/profile/seyma.kalay" target="_blank">**Tableau:**</a></u> 
Conducting data visualization using Tableau Destop.</li>

<li><u><a href="https://seymakalay.github.io/unibg/powerbi.html" target="_blank">**Power BI:**</a></u> 
Projects that I have been working on.</li>


<u>**HTML**</u>
<li><u><a href="https://seymakalay.github.io/TableauViz/index.html" target="_blank">**TableauViz**</a></u> 
Combining Tableau, Rshiny, and HTML.</li>





<u>**R Software Packages**</u> 
<li><u> <a href="https://github.com/seymakalay/pomodoro" target="_blank"> **CRAN** *Pomodoro:* </a></u>
Comparison of predictive power. This package is intended to make
modeling and comparing the predictive powers easier based on the data-splits and all data set.</li> 
<li><u> <a href="https://github.com/seymakalay/pepe" target="_blank"> **CRAN** *Pepe:* </a></u>
Is intended to make descriptive statistics easier. </li>
<li> **CRAN** *Oregano:* 
Is intended to create Shiny Modules to make the visualization easier,
expected release late 2023. </li>

<u>**GitHub**</u>
<li><u><a href="https://github.com/seymakalay" target="_blank">**Repositories:**</a></u> 
 Current Github repositories.</li>

<u>**Publications**</u> 
<li><u><a href="./pomodoro.pdf" target="_blank">  **Pomodoro:** </a></u> 
Predictive Power of Linear and Tree Modeling.</li>

<li><u> <a href="./pepe.pdf" target="_blank"> **Pepe:** </a> </u>
Data Manipulation. </li>



<!--\1   <u><a href="./Kalay_PHD_Presantation.pdf" target="_blank"> Phd-Dissertation </a></u>   \1--> 

<!--\1  \( \LaTeX \)  \1--> 

# Awards and Honors 

2017- 2022, UNIBG PhD Fund.\
DSU - Toscana, 2013 - 2016.\
TPV (Turkish Gas Foundation Scholarship), 2007 - 2010.\
Turkish Women Community Scholarship, 2007 - 2010.\
Yapi Kredi Bank Scholarship, 2006 - 2010.


# References

Reference letters will be provided upon [request](mailto:seymakalay@hotmail.com).

<!--\1
**Asso. Prof.:** Daniel Felix Ahelegbey; University of Pavia; Associate Professor; dfkahey@hotmail.com\
**Trading Mgr:** Birkan Karatas; Ziraat Portfoy; Trading Manager; bkaratas@ziraatportfoy.com.tr\
**Prof.:** Claudio Pacati; University of Siena; Full Professor; claudio.pacati@unisi.it\
\1--> 


<!--\1   <a href="#top">Back to top</a> \1-->
 <a href="#top" style="color:steelblue;" >Back to top</a> [`r fa("arrow-up", height = "2em", width = "1em", fill = "steelblue")`](#) 



